Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system of plausible mechanism

### 2024-10-17 _tex/index.tex
Built site for gh-pages

Over the past decade, numerous studies have documented the effectiveness
of the \emph{comparative judgment} (CJ) method
\citep{Thurstone_1927, Pollitt_2012a} for assessing competencies and
traits. These studies have examined the method's strengths from two main
perspectives: its capacity to produce reliable and valid trait scores,
and its practical applicability. In terms of reliability and validity,
research indicates that CJ generates precise and consistent scores that
accurately represent the traits being measured. Key contributions in
this area include those by \citet{Bramley_2008}, \citet{Pollitt_2012b},
\citet{Whitehouse_2012}, \citet{Lesterhuis_2018},
\citet{vanDaal_et_al_2019}, \citet{Bramley_et_al_2019},
\citet{Verhavert_et_al_2019}, \citet{Crompvoets_et_al_2022}, and
\citet{Bouwer_et_al_2023}. Regarding practical applicability, several
studies have demonstrated the method's versatility in both educational
and non-educational settings, offering an efficient and effective
alternative for measurement and evaluation. Notable examples include the
works of \citet{Jones_2015}, \citet{Bartholomew_et_al_2018},
\citet{Jones_et_al_2019}, \citet{Marshall_et_al_2020},
\citet{Bartholomew_et_al_2020}, and \citet{Boonen_et_al_2020}.

>>>>

Over the past decade, numerous studies have documented the effectiveness
of the \emph{comparative judgment} (CJ) method \citep{Thurstone_1927}
for assessing competencies and traits. These studies have evaluated CJ
from two main perspectives: its ability to produce reliable and valid
trait scores, and its practical applicability. In terms of reliability
and validity, research has shown that CJ can generate precise and
consistent scores that accurately represent the traits being measured.
Notable contributions in this research area include studies by Pollit
\citetext{\citeyear{Pollitt_2012a}; \citeyear{Pollitt_2012b}},
\citet{Whitehouse_2012}, \citet{vanDaal_et_al_2016},
\citet{Lesterhuis_2018}, \citet{Bramley_et_al_2019},
\citet{Verhavert_et_al_2019}, \citet{Crompvoets_et_al_2022}, and
\citet{Bouwer_et_al_2023}. Regarding practical applicability, several
studies have highlighted the method's versatility in both educational
and non-educational contexts, presenting it as an efficient and
effective alternative for measurement and evaluation. Key examples in
this research area include the works of \citet{Jones_2015},
\citet{Bartholomew_et_al_2018}, \citet{Jones_et_al_2019},
\citet{Marshall_et_al_2020}, \citet{Bartholomew_et_al_2020}, and
\citet{Boonen_et_al_2020}.

Despite the growing number of CJ studies, the unsystematic and
fragmented research approaches employed in the literature have
overlooked several critical issues concerning CJ. These issues can be
categorized into concerns about the method's structural model,
measurement model, and experimental design.

A key issue in the first category is the apparent disconnect between the
method's structural and measurement models. A common practice in CJ
literature involves performing data analysis and hypothesis testing on
scores previously estimated using the Bradley-Terry-Luce (BTL) model
\citep{Bradley_et_al_1952, Luce_1959}. These studies use the scores or
their transformations to identify `misfit' judges and stimuli
\citep{Pollitt_2012b, vanDaal_et_al_2017}, detect `bias' in judges'
ratings \citep{Pollitt_et_al_2003, Pollitt_2012b}, or test various
hypothesis
\citep{Bramley_et_al_2019, Boonen_et_al_2020, Bouwer_et_al_2023, vanDaal_et_al_2017, Jones_et_al_2019, Gijsen_et_al_2021}.
However, since CJ scores are parameter estimates with inherent
uncertainty, the statistical literature suggests that separating the
analysis from this uncertainty may artificially inflate the precision
and power of the results. This, in turn, could increase the risk of
committing a type I error, where a null hypothesis is wrongly rejected
\citep{McElreath_2020}.
